Pre-processing high frequency animal tracking data

### 2020-09-18 03_smoothing_tracks.Rmd
new figures

```{r read_sim_data_2}
# read in the data
data <- fread("data/data_sim.csv")

# add small position errors to either X or Y
data_with_errors <- copy(data)
data_with_errors[, `:=`(x = x + rnorm(nrow(data), mean = 0, sd = 0.005),
                        y = y + rnorm(nrow(data), mean = 0, sd = 0.005))]

# plot for sanity
ggplot()+
  geom_point(data = data_with_errors,
             aes(x, y),
             shape = 16,
             size = 0.2)+
  theme_void()
```

@@

```{r}
# make a copy
data_median_smooth <- copy(data_with_errors)
data_median_smooth <- atl_median_smooth(data_median_smooth,
                                        x = "x", 
                                        y = "y",
                                        time = "time",
                                        moving_window = 5)

# plot for sanity
ggplot()+
  geom_path(data = data,
            aes(x, y),
            colour = "blue",
            size = 2)+
  geom_point(data = data_with_errors,
             aes(x, y),
             shape = 16,
             size = 0.2)+
  geom_path(data = data_median_smooth,
            aes(x, y),
            colour = "red",
            size = 1)+
  theme_void()
```

>>>>

```{r read_sim_data_2}
# read in the data
data <- fread("data/data_sim.csv")[5000:10000, ]
data[, window_size := NA]
# data with small scale errors but no reflections or outliers
data_errors <- fread("data/data_no_reflection.csv")
data_errors[, window_size := 0]
```

@@

```{r}
# smooth the data
list_of_smooths <- lapply(c(3, 5, 11, 21), function(z) {
  data_copy <- copy(data_errors)
  data_copy <- atl_median_smooth(data = data_copy,
                    x = "x", 
                    y = "y",
                    time = "time",
                    moving_window = z)
  data_copy[, window_size := z]
})
```

```{r}
# prepare data to plot
# make list of data to plot
data_plot <- append(list(data, data_errors), list_of_smooths)

# add offset
data_plot <- mapply(FUN = function(df, offset) {
  df[, x := x + offset]
}, data_plot, seq(from = 0, to = 1, length.out = length(data_plot)),
SIMPLIFY = FALSE)

# bind rows
data_plot <- rbindlist(data_plot, fill = TRUE)

plot_figure <- ggplot()+
  # geom_point(data = data_plot,
  #            aes(x, y),
  #            col = "darkgrey", 
  #            alpha = 1,
  #            shape = 1)+
  geom_path(data = data_plot,
            aes(x, y, 
                col = window_size,
                group = window_size),
            alpha = 1,
            show.legend = FALSE)+
  annotate(x = 0.6 + seq(0, 1, length.out = 6),
           y = 1.05,
           label = glue::glue('({letters[seq(6)]})'),
           geom = "text",
           fontface = "bold")+
  scale_colour_viridis_c(option = "D",
                         na.value = "red")+
  coord_equal() +
  theme_test()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())

plot_figure

# save figure
ggsave(plot_figure, filename = "figures/fig_median_smooth.png",
       width = 185, height = 185 * 2 / 3, units = "mm")
```

## Aggregating data

```{r}
# choose the data
data_agg <- copy(data)

list_of_agg <- lapply(c(10, 30, 120), function(z) {
  data_agg <- atl_thin_data(data = data_agg,
                            interval = z,
                            method = "aggregate")
  data_agg[, interval := z]

})
```

```{r}
# plot
data_plot <- append(list(data[, `:=`(SD = 0, interval = NA)]), list_of_agg)

# add offset
data_plot <- mapply(FUN = function(df, offset) {
  df[, x := x + offset]
}, data_plot, seq(from = 0, to = 1, length.out = length(data_plot)),
SIMPLIFY = FALSE)

data_plot <- rbindlist(data_plot, fill = TRUE)

plot_figure <- ggplot(data = data_plot)+
  geom_point(aes(x, y, size = SD),
             colour = "darkblue",
             alpha = 0.5,
             shape = 16, show.legend = F)+
  geom_path(aes(x, y,
                group = interval,
                col = interval),
            col = "red",
            show.legend = FALSE)+
  annotate(x = 0.6 + seq(0, 1, length.out = 4),
           y = 1.05,
           label = glue::glue('({letters[seq(4)]})'),
           geom = "text",
           fontface = "bold")+
  coord_equal()+
  theme_test()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())

plot_figure

# save figure
ggsave(plot_figure, filename = "figures/fig_aggregate_data.png",
       width = 185, height = 90, units = "mm")
```
